### 2020-08-15 thesis/chap_1.tex
change imp value

\begin{table}[h!]
\centering
\caption{Variable importance (gini impurity index) for both random forest models - non-categorical variables only.}
\label{tab:varimp}
\begin{tabular}{lcc}
\hline
\hline
\multicolumn{1}{c}{\multirow{2}{*}{Variable}} & \multicolumn{2}{c}{Model} \\ \cline{2-3} 
\multicolumn{1}{c}{} & \multicolumn{1}{l}{Urbanisation} & \multicolumn{1}{l}{Agricultural expansion} \\ \hline
Distance from urban land & 756.8292 & 1787.357 \\
Size of forest patch & 548.5826 & 5373.270 \\
Elevation & 580.9726 & 1823.918 \\
Population change & 447.1120 & 1138.319 \\
Income & 390.5668 & 1108.612 \\ 
\hline
\end{tabular}
%\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{Variable importance (gini impurity index) for both random forest models - non-categorical variables only (rounded to nearest integer).}
\label{tab:varimp}
\begin{tabular}{lcc}
\hline
\hline
\multicolumn{1}{c}{\multirow{2}{*}{Variable}} & \multicolumn{2}{c}{Model} \\ \cline{2-3} 
\multicolumn{1}{c}{} & \multicolumn{1}{l}{Urbanisation} & \multicolumn{1}{l}{Agricultural expansion} \\ \hline
Distance from urban land & 2118 & 571 \\
Size of forest patch & 409 & 8424 \\
Elevation & 184 & 796 \\
Population change & 332 & 297 \\
Income & 371 & 315 \\ 
\hline
\end{tabular}
%\end{table}
